Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-26 draft/paper1_jenny.tex
New figure 3

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
      \caption{              
          \textbf{Top:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass differences along with the standard deviations
      	  in a series of mass bins are shown in large red, hexagons with error bars. 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Middle:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and does not show 
          clear mass--dependence. 
          \textbf{Bottom:} Difference between the \mtot{} and \mgama{} in the same
          format.  
          Here \mgama{} is based on single-\ser{} model derived from SDSS images. 
          }
      \label{fig:mass_diff}
  \end{figure}

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass differences along with the standard deviations
      	  in a series of mass bins are shown in large red, hexagons with error bars. 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and does not show 
          clear mass--dependence. 
          }
      \label{fig:mass_diff}
  \end{figure*}

@@
